On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-06 arity1pyramid.tex
Add files via upload

The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where 
\begin{itemize}
	\item $\mathrm{row}_1=(24136857)^{(k-1)/2}241$ if $k$ is odd, and $\mathrm{row}_1=(68572413)^{k/2-1}6857241$ if $k$ is even;
	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, that is each row is the reverse of the previous without the first and last bead.
\end{itemize}

@@

Stabilizing the first bead of row $j$ goes as follows (see Fig.~\ref{CI:turn}):
%\begin{itemize}
%	\item $\bf j\equiv 1\mod 4$: the first two beads are $24$, and the preceding bead is stabilized at $(4k-\frac{j-1}{2}, j-1)$. The $2$ can only bind to the $2$ which occurred two beads before at $(4k-\frac{j+1}{2}, j-1)$, and $4$ cannot bind anywhere, so the $2$ is stabilized at $(4k-\frac{j-1}{2},j)$.
%\end{itemize}

\begin{center}
	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
		%\renewcommand{\arraystretch}{2}
	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
						\hline
	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
	\hline
	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
	\hline
	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
	\hline
	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
	\hline		
	\end{tabular}
\end{center}

@@

		(c) Portions of row $1$
	\end{minipage}
	\caption{Fixing transcript beads in odd rows}
	\label{CI:1-4}
\end{figure}

As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1$ and $3$ bind to a bead in row $j-1$. In rows $j\equiv 2,4\mod 4$ beads of type $2$ and $4$ can bind to a bead in row $j-1$.  This is true for row $1$, because beads of type $1$ and $3$ from row $1$ can only bind to every second bead of the seed, whereas beads of type $2$ and $4$ from row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)). Once this dynamic holds for a row, it holds inductively for the next, as a bead that binds to another loses its only free hand at arity $1$.

Within one row of the transcript, no bead can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of four and the system has delay $2$.

>>>>

The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where 
\begin{itemize}
	\item $\mathrm{row}_1=(24136857)^{(k-1)/2}241$ if $k$ is odd, and $\mathrm{row}_1=(68572413)^{k/2-1}6857241$ if $k$ is even;
	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, where $w^r$ is the reverse of $w$. In other words, each row is the reverse of the previous without its first and last bead.
\end{itemize}

@@

Stabilizing the first bead of a row goes by binding to the penultimate bead of the previous row, as they are of the same type according to how we constructed the transcript, and they have free hands (see Fig.~\ref{CI:turn}).
%\begin{itemize}
%	\item $\bf j\equiv 1\mod 4$: the first two beads are $24$, and the preceding bead is stabilized at $(4k-\frac{j-1}{2}, j-1)$. The $2$ can only bind to the $2$ which occurred two beads before at $(4k-\frac{j+1}{2}, j-1)$, and $4$ cannot bind anywhere, so the $2$ is stabilized at $(4k-\frac{j-1}{2},j)$.
%\end{itemize}

%\begin{center}
%	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
%		%\renewcommand{\arraystretch}{2}
%	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
%						\hline
%	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
%	\hline
%	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
%	\hline
%	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
%	\hline
%	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
%	\hline		
%	\end{tabular}
%\end{center}

@@

		(c) Portions of row $1$
	\end{minipage}
	\caption{Fixing transcript beads in first row, when $k$ is odd}
	\label{CI:1-4}
\end{figure}

As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1,2,5,6$ bind to a bead in row $j-1$. In rows $j\equiv 2,4\mod 4$ beads of type $3,4,7,8$ can bind to a bead in row $j-1$.  This is true for row $1$, because beads of type $1,2,5,6$ from row $1$ can only bind to every second bead of the seed, whereas the other beads of row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)). Once this dynamic holds for a row, it holds inductively for the next, as a bead that binds to another loses its only free hand at arity $1$.

Within one row of the transcript, no bead $i$ can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of at least $6$ from any point where $i$ could be placed.
